Type Flattening Obfuscation

### 2020-01-30 paper/tool.tex
update

	% We show that the techniques used for type reconstruction can be bypassed,
	% and we claim that the bypass is always possible given \emph{semantics gap} between
	% type systems of high-level and machine language.
	% \keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{Introduction}
An important step in binary code \emph{decompilation}~\cite{cifuentes_reverse_1994} is to
detect high-level objects (e.g. functions, variables) from low-level machine dependent
objects~\cite{balakrishnan_divine_2007} (e.g. registers, raw memory accesses, machine
instructions) before annotate them with types of the "assumed" original language.
In a statically typed language like C, the compiler does not preserve the high-level
type information in the generated machine code,
% Because most of information about high-level types is lost in compilation,
% the machine code
then the \emph{type recovery} (or type reconstruction) from machine code requires
special techniques, a survey up until 2015 can be referenced in~\cite{caballero_type_2016}.

@@

\emph{First}, type obfuscation is unsurprisingly a side effect of data or control flow obfuscation.
Indeed, type reconstruction algorithms need both data and control flow to build type constraints,
if any of them is hidden
then the algorithms cannot work correctly. Or if the function boundary is not found
(because of anti-disassembing tricks, for example), then high-level objects cannot be recognized.
\emph{Second}, high-level types seem too coarse to be worthy
of being protected, in many cases just knowing certain values of the input which make the program
exploitable is enough. But knowledge about types expands attack surfaces because more analysis
can be proceeded, beside decompilation see the survey~\cite{caballero_type_2016} for a
more complete list.
% We exploit the \emph{semantics gap}

\section{Type flattening compiler}
We present \emph{uCc}, an open source C compiler that explicitly obfuscates high-level types, \emph{uCc}'s
objective is to make reconstructing C types from machine codes harder.
The compiler is implemented in Rust, the source code and a brief user guide are given at (cite); different
from other code obfuscation implementations, \emph{uCc} uses cranelift~\cite{noauthor_cranelift_nodate}
as backend.

>>>>

	% We show that the techniques used for type reconstruction can be bypassed,
	% and we claim that the bypass is always possible given \emph{semantics gap} between
	% type systems of high-level and machine language.
	% \keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{Introduction}
An important step in binary code \emph{decompilation}~\cite{cifuentes_reverse_1994} is to
detect high-level objects (e.g. functions, variables) from low-level machine dependent
objects~\cite{balakrishnan_divine_2007} (e.g. registers, raw memory accesses, machine
instructions) before annotate them with types of the "assumed" original language.
In a statically typed language like C, the compiler does not preserve the high-level
type information in the generated machine code,
% Because most of information about high-level types is lost in compilation,
% the machine code
then the \emph{type reconstruction} (or type recovery) from machine code requires
special techniques, a survey up until 2015 can be referenced in~\cite{caballero_type_2016}.

@@

\emph{First}, type obfuscation is unsurprisingly a side effect of data or control flow obfuscation.
Indeed, type reconstruction algorithms need data and control flow to build type constraints,
if any of them is hidden
then the algorithms cannot work correctly. Or if the function boundary is not found
(because of anti-disassembing tricks, for example), then high-level objects cannot be recognized.
\emph{Second}, high-level types seem too coarse to be worthy
of being protected, in many cases just knowing certain values of the input which make the program
exploitable is enough. But knowledge about types expands attack surfaces because more analysis
can be proceeded, beside decompilation see the survey~\cite{caballero_type_2016} for a
more complete list.
% We exploit the \emph{semantics gap}

\section{Type flattening compiler}
We present \emph{uCc}, an open source C compiler that explicitly obfuscates high-level types, \emph{uCc}'s
objective is to make reconstructing C types from machine codes harder.
The compiler is implemented in Rust, the source code and a brief user guide are given at~\cite{ta_ucc_nodate};
different from other code obfuscation implementations, \emph{uCc} uses cranelift~\cite{noauthor_cranelift_nodate}
as backend.
